### 2022-06-19 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e08ecc2032f88252bc68360880c8d8160202cdba 🚀

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily The prediction of species interaction networks
is facilitated by graph embedding and transfer learning despite data
limitations}
\vskip 5em

>>>>

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Graph embedding and transfer learning can help
predict species interaction networks despite data limitations}
\vskip 5em

### 2022-06-19 preprint.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@e08ecc2032f88252bc68360880c8d8160202cdba 🚀

\noindent {\LARGE \textbf{\textsf{The prediction of species interaction
networks is facilitated by graph embedding and transfer learning despite
data limitations}}}

>>>>

\noindent {\LARGE \textbf{\textsf{Graph embedding and transfer learning
can help predict species interaction networks despite data
limitations}}}
